The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games

### 2025-04-23 _tex/paper.tex
Built site for gh-pages

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Modeling Persuasion Behaviors in Social Deduction Games},
  pdfauthor={First Author; Second Author},
  pdfkeywords={social deduction games, persuasion modeling, Werewolf
Among Us dataset, large language models, multimodal analysis},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Modeling Persuasion Behaviors in Social Deduction Games}
\author{First Author \and Second Author}
\date{2025-04-17}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games},
  pdfauthor={Bhavana Jonnalagadda; Riley Jones},
  pdfkeywords={social deduction games, persuasion modeling, Werewolf
Among Us dataset, large language models, multimodal analysis},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{The Werewolf Among Us: Humans vs LLMs in Multi-Agent Games}
\author{Bhavana Jonnalagadda \and Riley Jones}
\date{2025-04-23}
